Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-19 paper/paper.tex
MCCS + directed

?? Connected, not strongly connected. No directed graphs.

@@

We haven't discussed partial subgraphs, or connected directed.

>>>>

For MCCS we consider only undirected graphs (and so we treat directed edges in the inputs as being
undirected). For directed graphs, there is more that one notion of connectivity, and it is not clear
which should be selected---our approach extends easily to weakly connected directed graphs, but not
to the strongly connected case.

@@

We haven't discussed partial or weighted subgraphs, or strongly connected directed.
